---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Natalie Johnson"
date: "8/29/2019"
output: 
  html_document: 
    fig_height: 10
    fig_width: 20
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The data has 1846 rows and 3 columns. The 3 variables include dataset, x, and y. 

### Exercise 2


First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The shape of the data is a dinosaur.

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
The r value=-.0645 which suggests no linear correlation which is clear in visualization of the data.

### Exercise 3

Use the dinosaurus_dozen data frame and filter it for observations where data == "star"
```{r plot-star}
> star_data <- datasaurus_dozen %>%
+   filter(dataset == "star")
> 
> ggplot(data = star_data, mapping = aes(x = x, y = y)) +
+   geom_point()
```
The data was visualized using the ggplot function.


The r value was calculated between x and y.
```{r cor-star}
> star_data %>%
+   summarize(r = cor(x, y))
```
The r value= -.0630 The r-value of the star suggests no correlation and is even further away from -1 compared to the dinosaur r-value= -.0645

### Exercise 4

The new data frame circle_data was assigned to datasaurus_dozen and then filtered to only include observations where dataset== "circle". The data was visualized using the ggplot function. The columns of the data get mapped and another layer is added to the plot (+)to define what geometric shapes represent the observations.  

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```
r value= -.0683 The r-value of the circle is closer to -1 then the r-value of the dino= -.0645 but clearly there is no linear correlation. 
### Exercise 5

All datasets were plotted at once using faceting. the colors were set by color=dataset. The geometric shape used was established by geom_point. ncol=3 created 3 columns and no legend was used. 

```{r plot-faceting}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) + 
  geom_point() + 
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```  

group_by was used to summarize the correlation coefficients of all the dataset. 

```{r cor-faceting}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
